On the Synchronization Power of the OpenFlow Data Plane

### 2015-05-26 inband-sync.tex
typos

Today, we do not have a good understanding yet of how to realize
such distributed control planes. The problem is essentially a
distributed systems
one: Multiple controllers may simultaneously try to
install conflicting updates and we want to resolve these conflicts
\emph{consistently} (no undesired behavior is observed on the data
plane) and \emph{efficiently} (no undesired delays are imposed on the
control application).
\emph{Synchronizing}
the distributed controllers and manipulating the network state \emph{consistently}~\cite{cpc}.
are non-trivial tasks~\cite{cap-theorem}.

>>>>

Today, we do not have a good understanding yet of how to realize
such distributed control planes. The problem is essentially a
distributed systems
one: Multiple controllers may simultaneously try to
install conflicting updates and we want to resolve these conflicts
\emph{consistently} (no undesired behavior is observed on the data
plane) and \emph{efficiently} (no undesired delays are imposed on the
control application).
\emph{Synchronizing}
the distributed controllers and manipulating the network state \emph{consistently}~\cite{cpc}
are non-trivial tasks~\cite{cap-theorem}.
